GSE158422: DNA methylation in Lung squamous cell carcinoma

### 2023-12-21 figs/GSE158422.Rmd
fix timeout

ARRAY_DATA="GSE158422_RAW.tar"
if(!file.exists(ARRAY_DATA)){
  options(timeout=10000000000000)
  download.file("https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE158422&format=file",
    destfile=ARRAY_DATA)
  untar(tarfile = ARRAY_DATA)
}

>>>>

ARRAY_DATA="GSE158422_RAW.tar"
if(!file.exists(ARRAY_DATA)){
  options(timeout=10000000000000)
  download.file("https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE158422&format=file",
    destfile=ARRAY_DATA)
}
untar(tarfile = ARRAY_DATA,exdir="IDAT")
